\section{Introduction}
%introduction of the topic
Algorithms are everywhere. They are a part of our everyday lives without even realizing it. They can be found in general mathematics, or in practical applications such as  computers or smartphones. But what exactly is an algorithm? According to the Oxford Dictionary an algorithm is generally speaken "a process or set of rules to be followed in calculations or other problem-solving operations, especially by a computer" (https://en.oxforddictionaries.com/definition/algorithm).
In our apprenticeship, we both have a lot to do with algorithms. Damian works as a software engineer, where he writes most of the time software. Stefan is an electronics engineer and his specialisation in the fourth year of education is also software. According to that, we both have a pretty good idea of what algorithms are and what they do. We found out, that each of us is fascinated by the concepts and possibilities algorithmic structures provide. So we came up with the idea, to implement an algorithm by ourselves.  \vspace{8mm}
%goals
We set the goal, to program an algorithm, that can play the game Ultimate TicTacToe (UTTT). UTTT is a more complex and strategic version of the ordinary TicTacToe. 
Our approach to solve that problem is a so called Self Learning Alpha Beta Pruning Algorithm, also known as SLAP Algorithm. It's a combination of the already existing Alpha Beta Pruning algorithm combined with an own made up extension which is, as the name suggests, self learning. We want to analyse the learning process of the algorithm in more detail and evaluate whether there is really an improvement. This will be the mathematical part of our work.
To experience our algorithm in action, we also wanted to create a website where everybody can play the game against our SLAP Algorithm.
Another intention of our project is to bring the seemingly complex subject in an easy understandable form to the interested reader. We aim to resume our approach of the solution in a comprehensible way. We want to give the reader an insight and a deeper understanding of algorithms, how they work and how they are implemented. With the website, we hope to create an interesting and interactive extension to this paper.
In order to meet the requirements to cover two subjects, we decided to write our paper and the website in English. \vspace{8mm}

%overview methodological approach
The first part of our IDPA will be to implement the game itself and the corresponding SLAP algorithm. 
That includes to find a way to value the states of the game in the most efficient way. This will be the task of the evolutionary algorithm. Only if that part of the SLAP algorithm works fine, the Alpha Beta Pruning is able to work in our favour.
We decided to realise all of that with a modern programming language called Dart from Google. Dart is a well-structured, object-oriented programming language that gives us the flexibility to write client and server-side code. All with one code base and one language. Once everything is set up, we will extend our project, that we are able to track the development of the self learning part. We are also planning to integrate a function into the website where the user can train his own SLAP algorithm and observe the progress themselves.
%overview structure of the paper
%to do

\section{Rules}
To understand to game Ultimate TicTacToe, it is required to  know the rules of the ordinary TicTacToe game. If you know the rules, you can continue reading the next paragraph. 

\subsection {Rules Tic Tac Toe}
The game Tic Tac Toe consist of a 3-by-3 board. Two players are required while one player represents X and the the other player represents O. One player can start and put his mark anywhere he'd like to. After that, the other player can take his turn and put his mark to a remaining spot. This procedure continues until someone has 3 of his own marks vertically, horizontally or diagonal aligned. It's possible that no party wins and the match ends undecided.

\subsection {Rules Ultimate Tic Tac Toe}
The board of Ultimate Tic Tac Toe is made up from a 9 ordinary Tic Tac Toe boards, hence there are 81 possible fields.
Each small Tic Tac Toe board will be called a local board and the big Tic Tac Toe board will be called the global board.
A player can start anywhere he'd like to on a local board. According to the location he played on a local board, his opponent will be sent to that position in the global board. The opponent can now play on the local board, keeping in mind that he will send the other player to the relative position on the global board. 

A victory of a local board is the equivalent to a marked tile on the global board. To win the game, one has to win 3 horizontally, vertically or diagonal aligned tiles of the global board.

If a local board is won or draw, no more moves are allowed there. In case a player was sent to such a board, he is allowed to make his next turn on every other local board. It's possible that the game ends in a draw, because  no more legal moves are allowed.

\section{SLAP Algorithm}
\subsection{Alpha Beta}
\subsection{Self Learning}
\subsection{Implementation in Dart}

\section{Progress Evaluation}
\subsection{win rate}

\section{Review}