\acsetup{first-style=short}
\acsetup{first-style=footnote}

\DeclareAcronym{UTTT}{
	short=UTTT,
	long=Ultimate Tic-Tac-Toe,
}

\DeclareAcronym{organism}{
	short=organism,
	short-plural-form=organisms,
	long=The organism contains the DNA and is part of a generation.,
}

\DeclareAcronym{generation}{
	short=generation,
	short-plural-form=generations,
	long=A generation contains several organisms.,
}

\DeclareAcronym{era}{
	short=era,
	short-plural-form=Era,
	long={An era is a set of generations and represents the Self Learning part of our SLAP algorithm.},
}

\DeclareAcronym{SLAP}{
	short=SLAP,
	long=Self Learning Alpha Beta Pruning,
}

\DeclareAcronym{SL}{
	short=SL,
	long=Self Learning,
}

\DeclareAcronym{ABP}{
	short=ABP,
	long=Alpha Beta Pruning,
}

\DeclareAcronym{DNA}{
	short=DNA,
	long={A mutable factor, which dictates the importance of a condition.},
}

\DeclareAcronym{condition}{
	short=condition,
	short-plural-form=conditions,
	long={In our context, a condition is a heuristic parameter. In our heuristic, exactly five conditions exist.},
}

\DeclareAcronym{heuristic}{
	short=heuristic,
	long={With the heuristic, we evaluate a meaningful number, which corresponds with an arbitrary game state.},
}

\DeclareAcronym{thread}{
	short=thread,
	long={A thread is a single unit of execution within a process. Normally, one thread at a time is executed by one core of a processor. },
}

\DeclareAcronym{UI}{
	short=UI,
	long=User Interface,
}

\DeclareAcronym{responsive}{
	short=responsive,
	long={A design pattern, especially for websites, which enables the User Interface to 		adapt according to different display resolutions and ratios of the end device (for example smartphones or desktop computers).} ,
}

\DeclareAcronym{BMS}{
	short=BMS,
	long=Berufs Mittel Schule,
}

\DeclareAcronym{IDPA}{
	short=IDPA,
	long=InterDisziplinäre Projekt Arbeit,
}

\DeclareAcronym{game state}{
	short=game state,
	long={A game state is any possible configuration on the UTTT field.},
}
